Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Commented code on QuickCheck -> /dev/null

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \subsection{QuickCheck}

%% \emph{TBD What does this have to do with the topic of the paper?}
%% \emph{Acknowledgment is enough.}

%% It is enough to test non-quantified properties just one.
%% However, QuickCheck 2.3 or earlier tests
%% non-quantified properties 100 times.
%% More precisely, the evaluation results are memorized and they are
%% compared with {\tt True} 100 times.
%% The current maintainer of QuickCheck modified so that
%% non-quantified properties
%% are tested just once in its source repository.
%% This feature will be available in the future release.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Doctest}
\label{sec:doctest}

@@

\noindent All combinators introduced in Section~\ref{sec:code-doc} have been
implemented.  They are available form Hackage\footnote{%
http://hackage.haskell.org/package/test-shouldbe},
and they will be incorporated into a future
release of Hspec.
The implementation is straightforward, so we will not further discuss
it.

@@

A fully functional implementations is available from
Hackage\footnote{http://hackage.haskell.org/package/hspec-discover},
and it will be incorporate into a future release of Hspec.

>>>>

\subsection{Doctest}
\label{sec:doctest}

@@

\noindent All combinators introduced in Section~\ref{sec:code-doc} have been
implemented.  They are available from Hackage\footnote{%
http://hackage.haskell.org/package/test-shouldbe},
and will be incorporated into a future
release of Hspec.
The implementation is straightforward, so we will not further discuss
it.

@@

A fully functional implementation is available from
Hackage\footnote{http://hackage.haskell.org/package/hspec-discover},
and it will be incorporated into a future release of Hspec.
